Covariates analysis of MSBB RNASeq data

### 2016-01-25 code/Rmd/MSSM_RNASeq.Rmd
Minor modifications

>>>>

### Clustering residual data
```{r decompse.normalise.data2, fig.height=8, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(RESIDUAL.GENE_EXPRESSION, scale.=T)

tree = hclust(as.dist(t(RESIDUAL.GENE_EXPRESSION)))
cols = WGCNA::labels2colors(COVARIATES.tmp);
tmp = gsub('\\..*','',cols)
WGCNA::plotDendroAndColors(tree, 
                           colors = tmp, 
                           dendroLabels = FALSE, 
                           abHeight = 0.80, 
                           main = "Sample dendrogram",
                           groupLabels = colnames(COVARIATES.tmp))
```
